% PAGE BUDGET
%
%                          TARGET    CURRENT
%
% Abstract + Introduction  2         2
% Preliminaries            3         5 1/3
% Algorithm description    4         7
% Experiments              2 1/2     3
% Conclusions              1/3       1/2

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass[runningheads]{llncs}
\usepackage{graphicx}
%\usepackage{bm}
\usepackage{epstopdf}
\usepackage{url}
\usepackage[usenames]{xcolor}
\usepackage[vlined]{algorithm2e}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{array}
\usepackage{microtype}
\usepackage{cite}

\newcommand{\Jose}[1]{{\color{red} [[JOSE:: #1]]}}
\newcommand{\Leo}[1]{{\color{blue} [[LEO:: #1]]}}
\newcommand{\Meng}[1]{{\color{green} [[MENG:: #1]]}}
\newcommand{\Norbert}[1]{{\color{orange} [[NORBERT:: #1]]}}
 
\input{preamble}

\begin{document}


\title{Parallel Construction of Succinct Trees\thanks{This work was supported in part by Jos\'e Fuentes-Sepúlveda's scholarship, granted by Government of Canada.}}
\titlerunning{Parallel Construction of Succinct Trees}

\author{Leo Ferres\inst{1} \and Jos\'e Fuentes-Sep\'ulveda\inst{1} \and Meng He\inst{2} \and Norbert Zeh\inst{2}}

\authorrunning{Leo Ferres, Jos\'e Fuentes-Sep\'ulveda, Meng He, and Norbert Zeh} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Leo Ferres, Jos\'e Fuentes-Sep\'ulveda, Meng He, and Norbert Zeh}
%
\institute{Department of Computer Science, Universidad de Concepci\'on, Chile,\\
\email{\{lferres,jfuentess\}@udec.cl},
\and
Faculty of Computer Science, Dalhousie University, Canada,\\
\email{\{mhe,nzeh\}@cs.dal.ca}}
  

\maketitle              % typeset the title of the contribution

\begin{abstract}
Succinct representations of trees have been an elegant solution to make large trees fit in main memory while still supporting
navigational operations in constant time. However, the construction time of succinct trees remains a computational bottleneck. In this
paper, we introduce a practical parallel algorithm that improves the state of the art in succinct tree construction. Given a tree on
$n$ nodes stored as a sequence of balanced parentheses, the proposed algorithm can build a succinct tree representation in
$O(n/p+\lg p)$ time, where $p$ is the number of available processors. The constructed representation occupies $2n + o(n)$
bits of storage and supports a rich set of navigational operations in $O(\lg n)$ time. We tested the algorithm on a $64$-core
machine and on inputs of different sizes.
In these experiments, it achieved good parallel speedup.
We introduce another algorithm that takes $O(n/p + \lg p)$ time to construct
the balanced parenthesis representation of the input tree required by our
succinct tree construction algorithm.
\end{abstract}
%

%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% INTRODUCTION %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:introduction}
\input{introduction}


%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% PRELIMINARIES %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%

\section{Preliminaries}
\label{sec:relwork}
\input{relwork}

\subsubsection{Succinct trees.}
\label{subsec:suctrees}
\input{suctrees}

\subsubsection{Dynamic multithreading model.}
\label{subsec:dym}
\input{dym}

%\subsection{Multicore succinct data structures}
%\label{subsec:multicoreSDS}
%\input{multicoreSDS}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% MULTICORE SUCCINCT TREE %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Multicore Succinct Tree}
\label{sec:multicoreST}
\input{multicoreST}

\subsection{Parallel Succinct Tree}
\label{sec:PST}

\subsubsection{The idea}
\label{subsec:idea}
\input{multicoreSTIdea}

\subsubsection{Parallel Succinct Tree Algorithm}
\label{subsec:multicoreSTAlgorithm}
\input{multicoreSTAlgorithm}

\subsubsection{Theoretical Analysis}
\label{subsec:theoreticalAnalysis}
\input{theoreticalAnalysis}

%\subsection{Parallel Succinct Tree for Large Trees}
%\label{subsec:parallelLargeTrees}
%\input{parallelLargeTrees}

\subsection{Parallel Folklore Encoding Algorithm}
\label{subsec:parenthesesAlgorithm}
\input{parenthesesAlgorithm}
%%%%%%%%%%%%%%%%%%%%%%%
%%%%% EXPERIMENTS %%%%%
%%%%%%%%%%%%%%%%%%%%%%%

\section{Experimental Results}
\label{sec:exps}
\input{exps}

\subsection{Experimental Setup}
\label{subsec:experimentalSetup}
\input{setup}

\subsection{Results and Discussion}
\label{subsec:resultsDiscussion}
\input{resultsDiscussion}

%%%%%%%%%%%%%%%%%%%%%%
%%%%% CONCLUSION %%%%%
%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion and Future Work}
\label{sec:conclusion}
\input{conclusion}

\section*{Acknowledgements}

We would like to thank Diego Arroyuelo for discussions about the
implementation of succinct trees, Roberto As\'{i}n for letting us use
his machines to run our experiments, and finally Rodrigo C\'{a}novas
for helping us with reusing their data in
\cite{Navarro:2014:FFS:2620785.2601073}.

\bibliographystyle{splncs03}
\bibliography{sigproc}

\end{document}

